---
title           : "OSF Qualitative Preregistration Template"
shorttitle      : "Qualitative Preregistration"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author:
  - Author 1^[Institution One, author1@example.org]
  - Author 2^[Institution Two, author2@example.org]

output: bookdown::pdf_document2
---

```{r setup, include=FALSE, }
# To share code, set  "echo = TRUE" in desired blocks 
knitr::opts_chunk$set(echo = F)
```

```{r packages and data, include = FALSE}
# Load packages and data to be clear from the start

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  kableExtra, #for building HTML or LaTeX tables using knitr
  bibtex, #bib parser for bibliography databases
  fancyhdr # customized header & footer lines with LaTeX
)

```

<!-- 
The text surrounded by these arrows is for your information and is hidden when the final document is knitted.
-->

# Metadata

##  Description

<!--
Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. 

More info: The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration. 

This information will be searchable in the Registry view (if public) so make sure it is concise and contains the more pertinent information.
-->

Enter a description of your study here.

##	License

<!-- 
Select the license you wish to apply to this registration.

More info: for help choosing a license, please see: https://help.osf.io/hc/en-us/articles/360019739014-Licensing
-->

License type here

## Subjects

<!--
Select the related subjects for the current project from OSF form. Can enter those here or remove section entirely
-->

Subjects here

## Tags

<!--
Add keyword tags to the project to enhance discoverability. Can list here as one would list key words in abstract or remove section entirely
-->


# Study Information

## Research Aims

<!--

If relevant, please reflect on whether your aim is different across different domains (e.g. knowledge generation, policy development, community resourcing). If so, specify your aim for each domain that is relevant for your study.


If helpful, please indicate the type of aim (non-exhaustive list):
Exploring
Describing
Theory evaluating
Comparing
Understanding
-->

Please specify the overall purposes, objectives or aims of the research here.

## Research Question(s)

<!--
Please specify your research question or questions as they are guiding your research now. If relevant, you may also specify here any hypotheses to be assessed. The research questions may break down your aim into smaller, distinct inquiries. If relevant, you may distinguish between primary and secondary research questions or hypotheses.

Example: If it is your aim to explore the attitudes of caregivers towards Alzheimer patients in a local ward, your research questions could specify precisely what you plan to study; for instance, how ward staff tries to treat the patients with dignity or how the relationship between the patient and their family members or loved ones evolved since that patient was admitted to the ward.
-->

Specify your research question or questions here

## Anticipated Duration

<!--
Please indicate the estimated project start date (mm/yyyy) and estimated project end date (mm/yyyy).
-->

**Estimated Start Date:** mm/yyyy here

**Estimated End Date:** mm/yyyy here

# Design Plan

## Study Design 

<!--
Please provide a brief, overarching characterisation of the study design. Your response might consist of a succinct label (e.g., “case study” or “ethnography”) and/or a brief elaboration of that label’s meaning. A study may involve a combination of different designs, including a mix of quantitative and qualitative methods.
-->

Brief study design here

## Sampling and case selection strategy

<!--
Please describe your sampling or recruitment strategy (examples include, but are not limited to: purposive, snowball, theoretical, and maximum variation sampling) and/or your case selection strategy (examples include, but are not limited to: typical case, most similar case, most different case, diverse case, and deviant case). Please provide a short rationale for why you selected this type of strategy.
-->

Sampling and case selection strategy here

## Data Collection

### Data source(s) and data type(s)

<!--
Please describe the type(s) of data you will be using. In describing the data, distinguish between data that existed prior to your study (e.g. archival documents, newspaper articles, [social] media, secondary literature, or data collected for a different purpose than the current study) and original data (i.e. data that will be collected/generated for the current study).
-->

Data source and type here

### Data collection methods

<!--
Please describe your method of data collection or data generation. Examples of methods include (but are not restricted to) interviews, focus groups, enabling techniques, self-reports, field notes, diaries, (participative) observation, archival research, or mixed methods. Please provide a brief rationale for why you plan to use this particular data collection/generation method in your study.

-->

Data collection methods here

### Data collection tools, instruments or plans

<!--
Please describe or upload the tools, instruments or plans you will use in collecting or generating your data. Examples could be (but are not limited to): topic guide, interview questionnaire, focus group guide, observation scheme, creative tools (e.g. photos, videos, musical pieces, paintings, etc.), or a description of your archival search plans.
-->

Data collection tools, instruments or plans here

### Stopping criteria

<!--
Please describe the criteria or rationale behind when you will stop data generation or collection. Possible criteria include (but are not restricted to): data saturation*, when inclusion criteria are satisfied, resource constraints (e.g. time/funding), or when the analysis has produced an enriching answer to the research question(s).

Example: We follow Fusch & Ness (2005) and interpret saturation to be reached when there is enough information to replicate the study, the ability to obtain new information has been attained, and further coding is no longer feasible.
-->

Stopping criteria here

# Analysis Plan

## Data analysis approach

<!--
Please specify the type and details of your data analysis approach. Examples of approaches include (but are not limited to): narrative analysis, phenomenological analysis, thematic analysis, content analysis, psychoanalytic analysis, grounded theory, process tracing, comparative analysis, or discourse analysis. If multiple interpretations of your approach exist, please specify the version you will be using. Please provide a rationale for why your selected data analytic approach is appropriate given your study’s aim(s).

Example: If you indicated ‘phenomenological analysis’, you may want to specify the theorist whose approach you are following, e.g. “We use a phenomenological approach as explained by Colaizzi (1978)”; or if you indicated ‘content analysis’, a specification could be: “We apply inductive content analysis as described in Elo & Kyngäs (2008)”.
-->

Data analysis approach here

## Data analysis process

<!--
Please describe what your process of data analysis will look like. Questions to keep in mind could be (but are not limited to):
* who will be involved in the data analysis, and in what role?
* if relevant, indicate any procedures that will be used to turn “raw” data into analyzable form (e.g., a coding scheme)
* if relevant, indicate any evidentiary criteria that will be used to assess any hypotheses (e.g., what evidence will count as consistent or inconsistent with a given proposition)
* if relevant, what software or analytic tools will you use and how will you use them?

-->

Data analysis process here

## Credibility strategies

### Methodological integrity assurances 

List relevant examples here:
<!--
Examples include (but are not limited to):
Member checking
Triangulation with other data sources
Bringing in different perspectives
Have different researchers analyse the data
Consensus building among team members or 'interrater reliability'
Negative case analysis
Peer debriefing
Cross-checks for rivalling explanations
Bring in an 'auditor'
Reflexitivity
Verisimilitude
Emotionality
Personal Responsibility
An ethic of caring
Political praxis
Multivoiced texts
Dialogues with subjects
Other (please explain)
-->

### Strategy Rationale

<!--
Please provide a short rationale for why you selected particular strategies and how they are appropriate given your study’s aim(s) and approach, or specify your credibility strategies if not on the above list. (required)
-->

Rationale here

# Miscellaneous

## Positionality Statement

<!--
Feel free to reflect on your relation to or association with the studied phenomenon and your position in the research setting/field, including your academic/personal standpoints, assumptions and values. 
-->

Reflection on your positionality here


## Conflict of Interest

<!-- If there is a potential conflict of interest [whether you have a previous relationship with the studied phenomenon, and if you consider that there are previous positions or assumptions that may influence the present study] that can arise, you may want to report that here.
-->

Any conflict of interest here

## Other

<!--
any additional information that will be helpful for future readers would be appropriate here. 
-->

Enter any additional information not covered by other sections, or state not applicable. 

# References 

Enter any references used throughout the text here.



<!-- 
Attribution:

Qualitative Preregistration(Haven et al., 2020) template: https://osf.io/zab38/wiki/home/

Rmarkdown based on James Bartlett's ["OSF preregistration template"] (https://github.com/BartlettJE/bartlettje.github.io/blob/master/RMarkdown-scripts/OSF%20preregistration%20template.Rmd) 
-->
